Maximum Spanning Malt: Hiring World's Leading Dependency Parsers to Plant Indian Trees

### 2009-10-30 papers/2009-icon-hyderabad/paper.tex
Tak v teto podobe to odeslu Samarovi k posouzeni.

%\microsection{MST Parser}
\subsection{MST Parser}
\label{sec:mst}
The Maximum Spanning Tree (MST) parser \citep{mst} views the sentence as an directed complete graph with edges weighted by a feature scoring function. It finds for the graph the spanning tree that maximizes the weights of the edges. A multi-class classification algorithm called MIRA is used to compute the scoring function.

@@

The tree is constructed from the root down. We repeatedly add nodes whose winning parent candidates are already in the tree. If none of the remaining nodes meet this condition, we have to break a cycle. We do so by examining all unattached nodes. At each node we notice the votes of its current winning parent. Then we remove the least-scoring winner and go on with adding nodes until all nodes are attached or there is another cycle to break.

@@

\begin{table}[ht]
\begin{centering}
%\small
\begin{tabular}{l|l|l|l|l}
& \textbf{MST} & \textbf{Malt} & \textbf{DZ} & \textbf{Vote}\\
\hline
hi & 86.16 & 85.84 & 75.12 & \textbf{87.12}\\
bn & 85.70 & 84.71 & 54.38 & \textbf{86.19}\\
te & 79.85 & 80.89 & 45.78 & \textbf{82.37}\\
\end{tabular}
\caption{UAS on mixed data: MST and DZ use POS+case+vibhakti for all languages, Malt uses that for Hindi and POS only elsewhere. MST is now the best parser for hi and bn, which changes the voting weights.}
\label{tab:posmix2}
\end{centering}
\end{table}

@@

The tag string should contain both the chunk label and the POS tag. So far we wrongly assumed that POS always determins the chunk label. It is often so but not always, as exemplified in the Bangla chunk sequence \bn{তবে সুদীপ ওকে একদিন আড়ালে ডেকে বলেছিল কৌতূহল দেখালে তুমি উঁচুতে উঠতে অনিমেষ} \translit{tabe sudīpa oke ekadina āṛāle ḍeke balechila kautūhala dekhāle tumi um̃cute uṭhate animeša}. The words \bn{ডেকে} and \bn{দেখালে} are tagged VGNF|VM while \bn{বলেছিল} and \bn{উঠতে} are VGF|VM. The parser gets them wrong and it could be caused by it seeing only VM in the tag.

@@

We have described our system of voting parsers, as applied to the ICON 2009 NLP Tools Contest task. We showed that case and vibhakti are important features at least for parsing Hindi while their usability in Bangla and Telugu is limited by data sparseness. We also discussed several error patterns that could lead to further improvements of the parsing system in future.

>>>>

%\microsection{MST Parser}
\subsection{MST Parser}
\label{sec:mst}
The Maximum Spanning Tree (MST) parser \citep{mst} views the sentence as a directed complete graph with edges weighted by a feature scoring function. It finds for the graph the spanning tree that maximizes the weights of the edges. A multi-class classification algorithm called MIRA is used to compute the scoring function.

@@

The tree is constructed from the root down. We repeatedly add nodes whose winning parent candidates are already in the tree. If none of the remaining nodes meet this condition, we have to break a cycle. We do so by examining all unattached nodes. At each node we note the votes of its current winning parent. Then we remove the least-scoring winner and go on with adding nodes until all nodes are attached or there is another cycle to break.

@@

\begin{table}[ht]
\begin{centering}
%\small
\begin{tabular}{l|l|l|l|l}
& \textbf{MST} & \textbf{Malt} & \textbf{DZ} & \textbf{Vote}\\
\hline
hi & 86.16 & 85.84 & 75.12 & \textbf{87.12}\\
bn & 85.70 & 84.71 & 54.38 & \textbf{86.19}\\
te & 79.85 & 80.89 & 45.78 & \textbf{82.37}\\
\end{tabular}
\caption{UAS on mixed data: MST and DZ use POS+case+vibhakti for all languages, Malt uses that for Hindi only, elsewhere it uses just POS.}
\label{tab:posmix2}
\end{centering}
\end{table}

@@

The tag string should contain both the chunk label and the POS tag. So far we wrongly assumed that POS always determines the chunk label. It is often so but not always, as exemplified in the Bangla chunk sequence \bn{তবে সুদীপ ওকে একদিন আড়ালে ডেকে বলেছিল কৌতূহল দেখালে তুমি উঁচুতে উঠতে অনিমেষ} \translit{tabe sudīpa oke ekadina āṛāle ḍeke balechila kautūhala dekhāle tumi um̃cute uṭhate animeša}. The words \bn{ডেকে} and \bn{দেখালে} are tagged VGNF|VM while \bn{বলেছিল} and \bn{উঠতে} are VGF|VM. The parser gets them wrong and it could be caused by it seeing only VM in the tag.

@@

We have described our system of voting parsers, as applied to the ICON 2009 NLP Tools Contest task. We showed that case and vibhakti are important features at least for parsing Hindi while their usability in Bangla and Telugu is limited by data sparseness. Providing these features to MST and DZ in all languages, and to Malt in Hindi only yielded the best combined parser. We also discussed several error patterns that could lead to further improvements of the parsing system in future.
